%% See the @yegor256 resume, boring version: https://github.com/yegor256/blog/blob/master/_latex/resume-boring.tex.
% See the Alex Zverev resume (PDF): https://drive.google.com/file/d/1dce28zy8RqS2O_27oj1rTYiZoFWZ3-Ot/view.

\documentclass[10pt]{article}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{blindtext}
\usepackage{enumitem}
\setlist[itemize]{noitemsep, topsep=4pt}

\usepackage{href-ul}

\usepackage{geometry}
\geometry{
    a4paper,
    left=20mm,
    %rigth=
    bottom=15mm,
    top=15mm
}

\usepackage{sectsty}

\sectionfont{
    \large % use smaller font for section instead of the default \Large;
    \fontfamily{qag}\selectfont % use \TeX Gyre Adventor font for sections instead of the default font for the entire document;
    \sectionrule{0pt}{0pt}{-5pt}{1pt} % print a horizontal rule 5pt below the title, with a thickness of 1 pt;
}

\pagestyle{empty}

%%% Macros

% size of the boxes used to align text
\newlength{\spacebox}
\settowidth{\spacebox}{123456789}

% macro: sepspace
\newcommand{\SectionSpacing}{ % vertical space separator between entries
    \vspace*{1em}
}

\newcommand{\SubSectionSpacing}{
    \vspace*{0.5em}
}

% macro: name
\newcommand{\name}[1]{%
    \Huge % font size
    % \fontfamily{phv}\selectfont % font family
    % print name centered and bold
    \begin{center} \textbf{#1} \end{center}\par
    % back to normal size and font
    \normalsize\normalfont%
}

% macro: experience
\newcommand{\Experience}[3]{%
    % name of the work
    \noindent \textbf{#1}
    % at the right the duration
    \hfill \text{#2} \par
    % new paragraph with the school in italics
    \noindent \textit{#3} \par
    % description with no hanging and in smaller text
    % \vspace*{0.5em}
    % \noindent\hangindent=2em\hangafter=0 \small #4 
    %back to normal size
    \normalsize \normalfont \par
}

% macro: Project
\newcommand{\Project}[3]{%
    \noindent \textbf{#1}
    \hfill \text{#2} \newline
    \small Source: \textit{#3}
    \vspace*{0.5em}
    \normalsize \normalfont \par
}

% macro: education 
\newcommand{\education}[3]{%
    \noindent  \textbf{#1}  %% academic degree
    \hfill  \text{#2} \par  %% duration, at the right
    \noindent \text{#3} \par %% university and deparment names, new paragraph
    \normalsize \par %% back to normal size
}

%%% Document

\begin{document}

\textsc{\huge{Nikita Khomitsevych}}

\SectionSpacing

\noindent
\href{mailto:hamsternik9@gmail.com}{hamsternik9@gmail.com} \text{\textbar}
\href{https://github.com/hamsternik}{github.com/hamsternik} \text{\textbar}
\href{https://www.linkedin.com/in/nkhomitsevych/}{linkedin.com/in/nkhomitsevych}

\SectionSpacing

\noindent
Software engineer with over 10 years of experience in developing software for Apple platforms (iOS, macOS, tvOS) and the frontend of web applications (React, Next).
For the past 5 years, I have exclusively worked in distributed software development teams. 
I have served as a team lead or as a software architect across various mobile and cross-functional projects. 
My primary areas of expertise include FinTech, Social, Healthcare, and Health \& Fitness.

%% Experience

\subsection*{Experience}

\Experience
{Senior iOS Engineer}
{Jul 2024 -- Jan 2025}
{\href{https://www.loblawdigital.co}{Loblaw Digital} (Top-1 Canadian retailer)}

\noindent
\begin{itemize}[label=-]
  \setlength\itemsep{0cm}
  \item Built a new \textbf{subscription mechanism for physical products} in stores, enabling users to subscribe to products they order consistently without needing to reorder manually each time.
  \item Developed the knowledge base for the iOS team using Coda.io, creating \textbf{dozens of internal documents} to structure the iOS app architecture by layers. 
  \item Led a technical proposal to introduce the \textbf{Single Responsibility Principle (SOLID)} by extending the MVVM architecture with the “UseCase” layer, streamlining unit test creation. 
\end{itemize}

\SubSectionSpacing

\Experience
{Software Engineer}
{Nov 2023 -- Jan 2025}
{\href{https://www.wurthy.co}{Wurthy} (Profitable solutions for growing businesses)}

\noindent
\begin{itemize}[label=-]
  \setlength\itemsep{0em}
  \item Developed a business web application (boost sales and generate monthly recurring revenue) and a customer web application (flexible checkout experience for buyers).
  \item Built both web apps using \textbf{Next.js 15, React v19, Tailwind, Postgres (Supabase), and Prisma ORM}.
  \item Built AI-driven customer workflows with \textbf{custom AI agents} to verify buyers' financial status and assess business risk profiles.
\end{itemize}

\SubSectionSpacing

\Experience
{Founding iOS Engineer}
{Jan 2023 -- Oct 2023}
{\href{https://www.wurthy.co}{Wurthy} (Make P2P payments over time)}

\noindent
\begin{itemize}[label=-]
  \setlength\itemsep{0em}
  \item Developed an MVP iOS application to deliver a brand-new \textbf{”Buy now, pay later" C2C} experience. 
    \textit{Sunset the iOS app} after the product pivot shifting to B2C PaaS.
  \item Managed a \textbf{team of 3 iOS engineers}. Led the technical aspects of the project.
  \item Established the minimal target tech stack for iOS 16+, including \textbf{SwiftUI, NavigationStack routing, async/await}. 
    Divided the codebase into Domain, Service, and Application modules.
\end{itemize}

\SubSectionSpacing

\Experience
{Software Engineer (Web Frontend, macOS)}
{Jun 2022 -- Nov 2022}
{\href{https://www.fluxon.com/}{Fluxon} (Product and outsourcing development distributed company)}

\noindent
\begin{itemize}[label=-]
    \setlength\itemsep{0em}
    \item Developed the front-end part of the \href{https://taki.app}{taki.app}. 
      Technologies included TypeScript, React, Next.js, GCP, Firebase and Firestore.
    \item Leaded the development of the \href{https://apps.apple.com/in/app/notiblast/id6443910263}{Notiblast} macOS application.
      App's goal is to remind about the upcoming meeting in your Google calendar, blasting upfront on your screen. 
      Technologies included Swift, SwiftUI / AppKit, Combine and XCTests.
\end{itemize}

\SubSectionSpacing

\Experience
{Senior iOS Engineer}
{Jan 2020 -- Apr 2022}
{\href{https://www.life360.com}{Life360 Inc.} (Family safety through location sharing)}

\noindent
\begin{itemize}[label=-]
    \setlength\itemsep{0em}
    \item Managed a \textbf{team of 4 mobile developers (Android and iOS)}, tackling requirements processing, delivery responsibilities and people management. 
    \item Developed Lead Generation feature to provide specific offers for customers from auto insurance companies (30+ million MAU, end of Q1 2022).
    \item Developed user's driving experience workflow, created brand new \textit{Driving} tab to see driving statistics and promote safe driving. 
      Technologies included Swift, UIKit, RxSwift, Uber RIBs, XCTests.
\end{itemize}

\SubSectionSpacing

\Experience
{iOS Software Engineer}
{Nov 2018 -- Dec 2019}
{\href{https://betterme.world/about}{BetterMe USA} (Personalized holistic wellness solution)}

\noindent
\begin{itemize}[label=-]
    \setlength\itemsep{0em}
    \item Most of my contributions were in the \href{https://apps.apple.com/us/app/betterme-weight-loss-workouts/id1264546236}{Health Coaching} and \href{https://apps.apple.com/us/app/betterme-calm-sleep-meditate/id1363010081}{Mental Health} apps including building both apps from scratch using the Redux architecture. 
      I also rewrote the entire BetterMe: Weight Loss Workouts app, transitioning it from VIPER to Redux.
    \item Developed a series of Fastlane scripts on Ruby to build an automated CI/CD pipeline, such as uploading new strings for localization in over 10 languages.
\end{itemize}

\SubSectionSpacing

\Experience
{iOS Software Engineer}
{Oct 2015 -- Sep 2018}
{\href{https://www.cybervisiontech.com}{CyberVision, Inc.}}

\noindent Project: \href{https://www.nuvocares.com/solutions}{Nuvo: applications for pregnant and doctor}.
\noindent
\begin{itemize}[label=-]
    \setlength\itemsep{0em}
    \item Developer iOS applications for manufactored FDA cleared device for remote nonstress tests for pregnant to monitor real-time health indicators.
    \item Architectured and developed a separated SDK to deal with device via Bluetooth Classic. Supported FDA and MFi device certification from engineering side.
    \item The application was designed to scale in mind using VIPER design pattern and BDD testing approach (Quick, Nimble).
\end{itemize}

%% Projects

\subsection*{Projects}

\Project
{Online Course \textbf{\href{https://robotdreams.cc/course/ios-razrabotka-prilozheniy-s-0}{iOS From Scratch}} [RU]}
{Feb 2021 -- May 2021}
{\href{https://github.com/hamsternik/robotdreams-ios-course}{hamsternik/robotdreams-ios-course}}

\noindent Created and taught a group of 12 students. 
The course included 20 lectures and a final assessment that outlined the requirements to follow and suggested thems for implementation. 
The course aimed to cover essential topics for iOS development, including Swift language fundamentals, memory management, UIKit iOS framework, concurrency (GCD) and networking basics.
The goal of the course was to prepare individuals without a computer science degree or prior programming experience for a \textit{junior iOS developer} position.

%% Education

\subsection*{Education}

\education
{Master's Degree in Computer Science}
{2013--2018}
{\href{https://kpi.ua/en}{Igor Sikorsky Kyiv Polytechnic Institute}, Biomedical Engineering Department}

\end{document}
