%% See the @yegor256 resume, boring version:
%%% https://github.com/yegor256/blog/blob/master/_latex/resume-boring.tex.
% See the Alex Zverev resume (PDF):
%%% https://drive.google.com/file/d/1dce28zy8RqS2O_27oj1rTYiZoFWZ3-Ot/view.

\documentclass[10pt]{article}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{blindtext}
\usepackage{enumitem}
\setlist[itemize]{noitemsep, topsep=4pt}

\usepackage{href-ul}

\usepackage{geometry}
\geometry{
    a4paper,
    left=20mm,
    %rigth=
    bottom=10mm,
    top=10mm
}

\usepackage{sectsty}

\sectionfont{
    \large % use smaller font for section instead of the default \Large;
    \fontfamily{qag}\selectfont % use \TeX Gyre Adventor font for sections instead of the default font for the entire document;
    \sectionrule{0pt}{0pt}{-5pt}{1pt} % print a horizontal rule 5pt below the title, with a thickness of 1 pt;
}

\pagestyle{empty}

%%% Macros

% size of the boxes used to align text
\newlength{\spacebox}
\settowidth{\spacebox}{123456789}

% macro: sepspace
\newcommand{\SectionSpacing}{ % vertical space separator between entries
    \vspace*{0.75em}
}

\newcommand{\SubSectionSpacing}{
    \vspace*{0.5em}
}

% macro: name
\newcommand{\name}[1]{%
    \Huge % font size
    % \fontfamily{phv}\selectfont % font family
    % print name centered and bold
    \begin{center} \textbf{#1} \end{center}\par
    % back to normal size and font
    \normalsize\normalfont%
}

% macro: experience
\newcommand{\Experience}[3]{%
    % name of the work
    \noindent \textbf{#1}
    % at the right the duration
    \hfill \text{#2} \par
    % new paragraph with the school in italics
    \noindent \textit{#3} \par
    % description with no hanging and in smaller text
    % \vspace*{0.5em}
    % \noindent\hangindent=2em\hangafter=0 \small #4 
    %back to normal size
    \normalsize \normalfont \par
}

% macro: education 
\newcommand{\education}[3]{%
    \noindent  \textbf{#1}  %% academic degree
    \hfill  \text{#2} \par  %% duration, at the right
    \noindent \text{#3} \par %% university and deparment names, new paragraph
    \normalsize \par %% back to normal size
}

%%% Document

\begin{document}

\textsc{\huge{Nikita Khomitsevych}}

\SectionSpacing

\noindent
\href{mailto:hamsternik9@gmail.com}{hamsternik9@gmail.com} \textbar\
\href{https://github.com/hamsternik}{github.com/hamsternik} \textbar\
\href{https://www.linkedin.com/in/nkhomitsevych/}{linkedin.com/in/nkhomitsevych}

\SectionSpacing

\noindent
Senior Software Engineer with 10+ years building and shipping products across
web and mobile platforms. Led engineering teams (up to 4 engineers), drove
architecture decisions in Healthcare, FinTech and Social domains. Currently
focused on full-stack development with React, Next.js, TypeScript and PostgreSQL.

%% Experience

\subsection*{Experience}

\Experience
{Senior Software Engineer}
{Jan 2025 — Present}
{\href{https://finitetimespace.com}{Finite Timespace LLC}}

\noindent
Provide hands-on engineering and technical consulting for businesses
and startups across web and mobile platforms.

\SubSectionSpacing

\Experience
{Software Engineer}
{Jan 2023 -- Jan 2025}
{\href{https://www.wurthy.co}{Wurthy} (Profitable solutions for growing businesses)}

\noindent
\begin{itemize}[label=-]
  \setlength\itemsep{0em}
\item Build two web applications -- a B2B dashboard (boosting
  sales, enabling MMR tracking) and a customer-facing checkout
  application. Stack: \textbf{Next.js, React 19, Tailwind, PostgreSQL,
  Supabase, Prisma ORM}.
\end{itemize}

\SubSectionSpacing

\Experience
{Software Engineer}
{Jun 2022 -- Nov 2022}
{\href{https://www.fluxon.com/}{Fluxon} (Global product development company)}

\noindent
\begin{itemize}[label=-]
  \setlength\itemsep{0em}
\item Developed the front-end part of the taki.app
  (https://taki.app). Tech stack comprises TypeScript, React, Next.js,
  GCP, Firebase, Firestore.
\end{itemize}

\SubSectionSpacing

\Experience
{Senior iOS Engineer}
{Jan 2020 -- Apr 2022}
{\href{https://www.life360.com}{Life360 Inc.} (Family safety through location sharing)}

\noindent
\begin{itemize}[label=-]
  \setlength\itemsep{0em}
\item Managed a \textbf{team of 4 mobile developers (Android and iOS)}, tackling requirements processing,
  delivery responsibilities and people management.
\item Designed and led the Lead Generation feature to provide \textbf{personalized auto insurance plans}
  for customers \textit{(30+ million MAU, end of Q1 2022)}.
\item Developed user's driving experience workflow, created brand new \textit{Driving} tab to see driving statistics
  and promote safe driving. Technologies included Swift, UIKit, RxSwift, Uber RIBs, XCTests.
\end{itemize}

\SubSectionSpacing

\Experience
{iOS Software Engineer}
{Nov 2018 -- Dec 2019}
{\href{https://betterme.world/about}{BetterMe USA} (Personalized holistic wellness solution)}

\noindent
\begin{itemize}[label=-]
  \setlength\itemsep{0em}
\item Build the \href{https://apps.apple.com/us/app/betterme-weight-loss-workouts/id1264546236}{Health
    Coaching} and \href{https://apps.apple.com/us/app/betterme-mental-health/id1363010081}{Mental
    Health} apps from scratch using \textbf{Redux architecture}.
\item Migrated the Mental Health app from VIPER to \href{https://github.com/betterme-dev/ReduxCore}{Redux architecture}.
\end{itemize}

\SubSectionSpacing

\Experience
{iOS Software Engineer}
{Oct 2015 -- Sep 2018}
{\href{https://www.cybervisiontech.com}{CyberVision, Inc.}}

\noindent Project: \href{https://www.nuvocares.com/solutions}{Nuvo:
  applications for pregnant women and doctor}.
\noindent
\begin{itemize}[label=-]
  \setlength\itemsep{0em}
\item Developed iOS applications for manufactured FDA cleared device
  for remote nonstress tests for pregnant women to monitor real-time health indicators.
\item Architected and developed a separate SDK to deal with device via Bluetooth Classic. Supported FDA and MFi device certification from engineering side.
\item The application was designed to scale in mind using VIPER design pattern and BDD testing approach (Quick, Nimble).
\end{itemize}

%% Tech Stack

\subsection*{Technical Stack}

\noindent \textbf{Full-stack}: React, Next.js, Node.js, TypeScript,
Tailwind CSS, PostgreSQL, Supabase, Prisma ORM, Jest.\\
\noindent \textbf{Tools}: Make, Fastlane, GitHub Actions.

%% Education

\subsection*{Education}

\education
{Master's Degree in Computer Science}
{2017--2018}
{\href{https://kpi.ua/en}{Igor Sikorsky Kyiv Polytechnic Institute}, Biomedical Engineering Department}

\end{document}
